Longitudinal data

### 2020-03-19 production/analysis-cfa.Rmd
update02

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: ../style.css
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

@@

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

>>>>

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

@@

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

### 2020-03-19 production/prep-data-A.Rmd
update02

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```
